\documentclass[letterpaper,oneside,10pt]{scrartcl}

\input{include/config} 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% DOCUMENT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\title{MUSI 4705/4699/7100: Syllabus}
\author{Music Technology Research Lab --- Music Informatics Group}
\date{Fall 2025} %%If commented, the current date is used.
\maketitle


\pagestyle{plain} %Now display headings: headings / fancy / ...

\section*{Course Details}
    \begin{tabular}{ll}
        \textbf{class time} & seminar M 14:00, group meeting W 14:00, individual meetings tbd \\
        \textbf{location} & seminar WV175, lab Couch 202, office SoA 266A\\
        \textbf{credits} & 3 credit hours\\
        \textbf{modality} & in person
    \end{tabular}
    
\section*{Instructor Information}
    \begin{tabular}{lll}
        %\textbf{} & \textbf{instructor} & \textbf{teaching assistant}\\
        \textbf{name} & Alexander Lerch & \\
        \textbf{email} & \url{alexander.lerch@gatech.edu} & \\
        \textbf{location} & SoA 266A (bridge between architecture buildings) & \\
        \textbf{office hours} & {by online appointment (\href{https://outlook.office.com/bookwithme/user/fd6fbed37b7c4ee8a3e25e7cdcbee3f5@gatech.edu?anonymous&ep=plink}{bookwithme online appointment})} & \\
    \end{tabular}

\section*{Group Communication}
    You will receive invitation links to the mailing lists below --- notify me if you don't or if you have any questions or concerns.
    
    \vspace{\baselineskip}
    \begin{tabular}{ll}
        \textbf{MS Teams Channels} & \\
        \textbf{musicinformatics@googlegroups.com} & internal: meetups, discussions, etc.  \\
        \textbf{music-informatics-alumni@googlegroups.com} & external: announcements \& accomplishments for all alumni  \\
        %\textbf{music-performance-analysis@googlegroups.com} & internal: FBA \& funded research 
    \end{tabular}
        
\section{General Information}        
    \subsection{Course Description}
        Guided research and creative work in music technology. Investigation of novel technological and artistic concepts with scientific methodologies. Experimental design and development of new algorithms, software, and musical artifacts.
        
    \subsection{Prerequisites}
        There are no formal prerequisites. Prior coursework in signals and systems and machine learning is expected. Programming experience and familiarity with Python will be helpful.

    \subsection{Learning Outcomes}
        After successful completion of the class, the students will demonstrate 
        \begin{itemize}
            \item   knowledge of state of the art algorithms and technology in music technology,
            \item   the ability to design and implement algorithms, and to design and implement systems for the analysis, synthesis, and/or processing of audio and music,
            \item   the ability to design and execute a systematic and meaningful evaluation methodology including appropriate selection and handling of data, evaluation procedure, and identification of suitable metrics,
            \item   the ability to plan for all stages of a research project (i.e., formulating the research question, doing a literature survey, finding/implementing a baseline/comparison, designing the experiment, evaluating and analyzing the results systematically), and 
            \item   the ability to present the results in a structured and clear, understandable way in scientific writing and a poster presentation.
        \end{itemize}
        
    \subsection{Course Modality Information}
        Personal \textbf{attendance is mandatory} in  the Monday seminar series (2pm) and the group meeting (TBA) unless announced otherwise. The individual meetings are by default scheduled in person but can be adapted to other formats if agreed on.
        
\section{Course Requirements \& Grading}
    The overall grade consists of:
    \smallskip
    
    \begin{tabular}{lll}
        \textbf{attendance} & 15\%\\
        \textbf{project work} & 50\%\\
        \textbf{paper} & 15\%\\
        \textbf{final (poster) presentation} & 20\% \\
    \end{tabular}
    
    \subsection{Description of Graded Components}
        Individual undergraduate students and capstone students will be graded identically but will receive a grade 10\% higher. Group projects will be graded identically to graduate students, but will have to submit an additional questionnaire about their and their team mates' contribution.
        \begin{itemize}
            \item   \textbf{attendance}:\\ participation in Monday seminars and in group meetings as well as in scheduled individual meetings (all mandatory)
            \item   \textbf{project work}:\\ your individual or group project for this semester. Grades will assigned according to quality, significance, and impact of your contributions to the project, the ability to complete assigned tasks in a timely manner, the ability to communicate and collaborate with others, and the innovations and ideas that shape the direction of our research.
            \item   \textbf{paper} (due date: before the final instructional class days):\\ conference style paper describing the project in a scientific style in a quality that would allow conference submission. Grades will be assigned according to structure, clarity, references, quality of information, and form. In addition, second year students will also provide a MS project proposal in a similar format at the begin of their 3rd semester.
            \item   \textbf{presentation}:\\ In addition to presenting your work in the lab meeting, there will be a research showcase at the end of the semester (assigned slot during final exam week) where you will present your work to other students and visitors. Second year students will also present their MS project or thesis in the Monday seminars. The presentation grade will be assigned according to the organization, completeness, verbal and non-verbal presentation skills, and the quality of the visual materials (structure, easy to read, visualizations, etc.).
        \end{itemize}
        
    \subsection{Grading and Grading Policies}
        \input{include/grading} 

    \section{Course Materials}

        \subsection{Software}
            \input{include/software} 
            
        \subsection{Course Management}
            The class will be managed through Canvas.
            
    %\section{Method of Evaluation}
        %The overall grade consists of:
        %\begin{itemize}
            %\item   \textbf{10\% }
            %\item   \textbf{50\% }
            %\item   \textbf{20\% }
            %\item   \textbf{20\% }
        %\end{itemize}
        %
        %%The winners of the video competition will receive additional points to be \textit{added to their final grade} (1st: 8 points, 2nd: 5 points, 3rd: 3 points).
        %
        %\subsection{Grading and Grading Policies}
            %\input{include/grading} 
\section{Course Schedule}
    The class schedule is based on weekly meetings: the weekly Monday seminar, weekly group meetings, as well as weekly individual meetings. Regular individual meetings (20 minutes) will be scheduled at the begin of the semester, time-slots will be available for additional (sign-up) appointments.
    
    Relevant information is available in our github repo: \url{https://github.gatech.edu/alerch3/MUSI7100-Projects}
    %
    Other information can be found in this repository as well, such as
    \begin{itemize}
        \item   lab meeting schedule:\\ \url{https://github.gatech.edu/alerch3/MUSI7100-Projects/blob/master/lab-meeting.md}
        \item   general info:\\ \url{https://github.gatech.edu/alerch3/MUSI7100-Projects/blob/master/readme.md}
        \item   GPU overview:\\ \url{https://github.gatech.edu/alerch3/MUSI7100-Projects/blob/master/lab-machines.md}
        \item   templates for slides and posters
    \end{itemize}
    
    %\input{include/schedule}

    
\section{Course Expectations \& Guidelines}
        
    %\subsection{Active Participation}
        %\input{include/attendance}

    %\subsection{Guthman Competition}
        %Every student is required to attend the Guthman competition concert on Saturday, March 8th at 7 pm at the Ferst Center ---for which you will receive a complimentary ticket--- and to 5sign up for a shift to assist at the competition on March 6, 7, or 8. The school of music also strongly encourages you to attend other Guthman events on March 7 and 8, including presentations by our finalists, a panel with our judges, and a music/art/tech fair at which you can share your own work. More details will be available later in the semester.
        
    \subsection{Extensions, Late Assignments, Missed Exams}
        \input{include/extensions}

    \subsection{Inclement Weather and Digital Learning Days}
        \input{include/weather}
        
    \subsection{Student Use of Mobile Devices in the Classroom}
        \input{include/mobile}
    
    \subsection{Academic Integrity}
        \input{include/integrity}

    \subsection{Accommodations for Individuals with Disabilities}
        \input{include/disabilities}
        
    \subsection{Use of Generative AI}
            \input{include/genai}
				
    \subsection{Digital Etiquette}
        \input{include/etiquette}

	\subsection{Student-Faculty Expectations}
        \input{include/expectations}
        
    \subsection{Diversity}
        \input{include/diversity}
        
    \subsection{Academic Grievance Policy}
        \input{include/grievance}
\end{document}

